My Findings

### 2024-06-14 Findings (Shared Folder)/Chapters/modelAttempts.tex
new results

\subsection{Simulation Domain}
to be expanded: square $ [0,1]\times [0,1] $. With the tumor located at $\set{1} \times [0,1] $ and the parent vessel located at $ \set{0} \times [0,1] $.

>>>>

\subsubsection{Simulation Domain}
The simulation domain is the square $ [0,1]\times [0,1] $. With the tumor located at $\set{1} \times [0,1] $ and the parent vessel located at $ \set{0} \times [0,1] $.

I implemented this model in the Visual PDE online solver, with the parameters that both their result look good and also the default solvers of this tool are stable. You can find the model \href{https://visualpde.com/sim/?options=N4IgRgqiBcIHYFMCuBbAhnOIA04BqM8y6mO4A6oYqhlrgMaEBuAlgE4sAmLAzmfQBEYAFzZIEuThCiwhkiAVgBaAAQANAPQAKAIwBqNACp6ASkN0QUysrbmynPIpAAGe+Wsv7fWDud-7wjDOAHR+AKy4AGYAkiJiEiD0MiAIAB4ADlpKIX46hqkAegBMZlo8LHBaAMyG6SyGWgCeGgAyAPqNJl3F-E5pmdmhfn41Wqkqqu2pJsUm-B79WTnDeWMzJWQA1oQCKgC8KjoA3Gr7KgBsfkdoZ8tHbGdhzkfpZ8dgt0NXAOafzmFHMjoQghKoAdiBLBBZCwsCqMIAKjAns5cOkEGxIgB7NgkegIACyWM4CDi4jRhAAwkgeMIsSgyOk2FiwAgAGJIWHwRnM1ktBBwb7CAAWMCqw1wbGSrklTiU6XMxjIbA8YEMkQmKm+isiZB46UIvj1XLgKnoKl1uB4AEcyQlhJw7bgmDAANqgOBoFCknxkLFMDEAGzQjQAohk2IaeSz2ZyqNHWWpoWjeQgAJrJkA8JCYtD4jlcmUgADuwrQwgRWIACoGsYFYFgAL7YUBoNjM4uUrG1nMwc5hMJVCIgNsdgQC8rCRpBYLD0dY4v8wUigloVJR3Dz4sAZXoaEDPpHSDpZC3SdgUw0RU16837YXGYvHSvmunm+PWO3CGEXZ7bAAShg3w+pE+48Ake7emwaAIsK35oGKqKJF6GJoFWwpQtA4oMCh0EAFpYvSM4ABwMN2WI5ugBqwKwHDcHwZF-mAbYwKBgbgWRcB0jm3hsRxiRYlxFFsL+wlBJx3FsKG6TlLWsI5DoEnCQAcqgyIMDSdIoNuOagfirFgQkCAoGAWI8Lxhm4MZpnmQAgiZLACvWITDtZZk8AILCRJENI+iE5xWSZ7noZhOizmCzikSkQXmduGFwNO0C+IFNk8NuKCESKiDmTORQpe527ovQSDBpG0AhHl0WpbB8EzmCxFhAALFEgYsOk6KcKJlFoNRfEJK1iDkFwK4lTAikgOgqRdWweD7uIILBOCkJwNNs2BvNsBFv6QYhgZ7EJNtbDBo003iSAh3HdJsmCTO4S4BdIbhkyG7nQGR0hi0FQIENnAjYGY1orWFaNOihDpMGiAJhU3x7fxTIxgW8YpjGS5CqKWESiA8OsgiIOHhUwgIN80H-cjiaZtj6aZtmub5nGm1kCKbAIAgAgABIICw3zCsIu77n5wRgs6CD0HSbBso5gaOtAfW4KW5aVjWdaEIwuCet6MBFM2rb3p25G9tA-aDnOuvjnAk6JS5d4dqjK5ri9W58wehBoB+p66+eICXteqi3iOuuPl7z4+yob5HnSX4-vrAFASBlnIVBMFwcICEYzhichYh6eoQRRHlcEUX0NHVHMOwXC8Pw0fMWVssCUJPGwxBgmSad5VKTmV0sHJt3jUX9dsKpDLQMOxW0vSOm03H+35TlMvx25dkOU5M6uTFHleT54EzgFVXBRhY3hZFM9pfFiXJbvsUZXWwrZd4FXH4VIslSx+eVQvPA1SndUNc1ICRK17UECdWLj1RuuABrfWGsKAko0kq4EmqtOah5QQQngRURB61kF+jesdMBr0donWjmdB6YYZJdxuvnO6+D3phgjC9Ehn1BpQJgf9OBWMga41BrAcGGBSRk2hngymiMGwJgQLbdG4o-BkwQJw-GXEiYk1EZ7IslNA5FhpnpWMhZGbCmZqzDmXMeZOwFkLEAAZRY4glggKWeD5YVmrEDQglp4AoTFI2AAunLaW3I5bUR8VmFgKAEQsGEM7WAtlBQsCxMBbKvBNQRJJDwQSKhKRlh4RUEAjYgA}{here}.
